### 2021-06-10 papers/thesis/full/ch2-spherical-harmonics/spherical-harmonics.tex
Addressed the new minor comments, though I have questions for the other points. Also changed the rec coeff mats defs for each chapter to make consistent.

These recurrences lead to Jacobi operators that correspond to multiplication by $x,y,z$ of the OPs. Define for $l \in \No$: \nomenclature[Pvector]{$\SHvec$}{Vector of the SH OPs} \nomenclature[Pvectorl]{$\SHvec_l$}{(Sub-)Vector of the degree $l$ SH OPs}
\bseqn{
	\SHvecl := 
		\begin{pmatrix}
			Y^{-l}_l \\
			\vdots \\
			Y^l_l
		\end{pmatrix} \in \C^{2l+1}, 
	\quad \quad 
	\SHvec := 
		\begin{pmatrix}
			\SHvec_0 \\
			\hline
			\SHvec_1 \\
			\hline
			\SHvec_2 \\
			\vdots \\
		\end{pmatrix}.
}
Note that these OP vectors we have defined are grouped and ordered according to the degree $l$, and within each degree ordered by the Fourier mode $m$. Let the Jacobi matrices \nomenclature[J]{$J_x, J_y, J_z$}{Jacobi operator matrices} $J_x, J_y, J_z$ hence be given by 
\bseqnnumber{
	J_x \SHvec(x,y,z) = x \SHvec(x,y,z), \quad J_y \SHvec(x,y,z) = y \SHvec(x,y,z), \quad J_z \SHvec(x,y,z) = z \SHvec(x,y,z) \label{eqn:jacobimatsdef}
}
for $(x,y,z) \in \Omega$. These Jacobi matrices can act on the coefficients vector of a function's expansion in the spherical harmonic basis to implement the operation for multiplication by $x$, $y$ or $z$. For example, given sufficiently large $n \in \N$ let the function $f(x,y,z) : \Omega \to \C$ be given by its expansion \nomenclature[fvec]{$\vec{f}, \vec{\xi}$}{Lower case bold letters refer to vectors} \nomenclature[transpose]{$\vec{v}^\top, A^\top$}{Transpose of the vector $\vec{v}$ or matrix $A$ (non complex conjuagate)}
\bseqn{
	f(x,y,z) = \sum_{l=0}^{N} \sum_{m=-l}^{l} f_{l,m} \; \Ylm(x,y,z) = \SHvec(x,y,z)^\top \: \fvec
}
where 
\bseqn{
	\fvec_l := 
		\begin{pmatrix}
			f_{l,-l} \\
			\vdots \\
			f_{l,-l}
		\end{pmatrix} \in \C^{2l+1}, 
	\quad \quad 
	\fvec := 
		\begin{pmatrix}
			\fvec_0 \\
			\vdots \\
			\fvec_N
		\end{pmatrix}.
}
We say that $\fvec$ is the \textit{coefficients vector} of the function $f$. Then $x f(x,y,z)$ is approximated by $\SHvec(x,y,z)^\top \: J_x^\top \: \fvec$. In other words, $J_x^\top \: \fvec$ is the coefficients vector for the expansion of the function $(x,y,z) \mapsto x \: f(x,y,z)$ in the spherical harmonics basis.

@@

Since the above holds for any $\Dlt$ that is a left inverse of $A_l$, we are free to choose the $\Dlt$ matrices in the following way. For $l \in \N$, we can set
\bseqnnumber{
	\Dlt = 
		\begin{pmatrix}
			& & & & & \vec{\eta}^\top_{0} \\
			0 & & & 0 & & & {1 \over \gamma_{l,-l,2}} & \\
			& \ddots & & & \ddots & & & \ddots \\
			& & 0 & & & 0 & & & {1 \over \gamma_{l,l,2}} \\
			& & & & & \vec{\eta}^\top_{1} 
		\end{pmatrix} \in \R^{(2n+3)\times3(2n+1)}, \label{eqn:Dltdef}
}
where $\vec{\eta}_{0}, \vec{\eta}_{1} \in \R^{3(2n+1)}$ are vectors with entries given by 
\bseqn{
	\big(\vec{\eta}_{0}\big)_j &= 
		\begin{cases}
			{1 \over \alpha_{l,-l,3}} & j = 1 \\
			{- \; \alpha_{l,-l,4} \over \alpha_{l,-l,3} \: \gamma_{l,1-l,2}} & j = 2(2n+1) + 2 \\
			0 & o/w
		\end{cases}, \\
	\big(\vec{\eta}_{1}\big)_j &= 
		\begin{cases}
			{1 \over \alpha_{l,l,4}} & j = 2l+1 \\
			{- \; \alpha_{l,l,3} \over \alpha_{l,l,4} \: \gamma_{l,l-1,2}} & j = 3(2n+1) - 1 \\
			0 & o/w
		\end{cases}.
}
For $l = 0$ we can simply set
\bseqnnumber{
	D^T_0 = 
		\begin{pmatrix}
			{\beta_{0,0,4} \over \alpha_{0,0,3} \beta_{0,0,4} - \alpha_{0,0,4} \beta_{0,0,3}} & {- \alpha_{0,0,4} \over \alpha_{0,0,3} \beta_{0,0,4} - \alpha_{0,0,4} \beta_{0,0,3}} & 0 \\
			0 & 0 & {1 \over \gamma_{0,0,2}} \\
			{\beta_{0,0,3} \over \alpha_{0,0,4} \beta_{0,0,3} - \alpha_{0,0,3} \beta_{0,0,4}} & {- \alpha_{0,0,3} \over \alpha_{0,0,4} \beta_{0,0,3} - \alpha_{0,0,3} \beta_{0,0,4}} & 0
		\end{pmatrix}. \label{eqn:Dzerotdef}
}
It will be convenient for us to give a formal name for these coefficient matrices above for a family of multidimensional orthogonal polynomials.
\begin{definition}\label{def:clenshawmats}
	The matrices $-\Dlt (B_l-G_l(x,y,z))$, $\Dlt C_l$ for $l \in \No$ defined via \bsrefeqns{eqn:clenshawmats1}{eqn:Dzerotdef} are called the \textbf{recurrence coefficient matrices} for a given family of multidimensional orthogonal polynomials.
\end{definition}

>>>>

These recurrences lead to Jacobi operators that correspond to multiplication by $x,y,z$ of the OPs. Define for $l \in \No$: \nomenclature[Pvector]{$\SHvec$}{Vector of the SH OPs} \nomenclature[Pvectorl]{$\SHvec_l$}{(Sub-)Vector of the degree $l$ SH OPs}
\bseqn{
	\SHvecl := 
		\begin{pmatrix}
			Y^{-l}_l \\
			\vdots \\
			Y^l_l
		\end{pmatrix} \in \C^{2l+1}, 
	\quad \quad 
	\SHvec := 
		\begin{pmatrix}
			\SHvec_0 \\
			\hline
			\SHvec_1 \\
			\hline
			\SHvec_2 \\
			\vdots \\
		\end{pmatrix}.
}
Note that these OP vectors we have defined are grouped and ordered according to the degree $l$, and within each degree ordered by the Fourier mode $m$. Let the Jacobi matrices \nomenclature[J]{$J_x, J_y, J_z$}{Jacobi operator matrices} $J_x, J_y, J_z$ hence be given by 
\bseqnnumber{
	J_x \SHvec(x,y,z) = x \SHvec(x,y,z), \quad J_y \SHvec(x,y,z) = y \SHvec(x,y,z), \quad J_z \SHvec(x,y,z) = z \SHvec(x,y,z) \label{eqn:jacobimatsdef}
}
for $(x,y,z) \in \Omega$. While $J_x, J_y, J_z$ are not Jacobi matrices in the classical sense, they are block Jacobi matrices. However, it is useful to simply label them as such. These Jacobi matrices can act on the coefficients vector of a function's expansion in the spherical harmonic basis to implement the operation for multiplication by $x$, $y$ or $z$. For example, given sufficiently large $n \in \N$ let the function $f(x,y,z) : \Omega \to \C$ be given by its expansion \nomenclature[fvec]{$\vec{f}, \vec{\xi}$}{Lower case bold letters refer to vectors} \nomenclature[transpose]{$\vec{v}^\top, A^\top$}{Transpose of the vector $\vec{v}$ or matrix $A$ (non complex conjuagate)}
\bseqn{
	f(x,y,z) = \sum_{l=0}^{N} \sum_{m=-l}^{l} f_{l,m} \; \Ylm(x,y,z) = \SHvec(x,y,z)^\top \: \fvec
}
where 
\bseqn{
	\fvec_l := 
		\begin{pmatrix}
			f_{l,-l} \\
			\vdots \\
			f_{l,-l}
		\end{pmatrix} \in \C^{2l+1}, 
	\quad \quad 
	\fvec := 
		\begin{pmatrix}
			\fvec_0 \\
			\vdots \\
			\fvec_N
		\end{pmatrix}.
}
We say that $\fvec$ is the \textit{coefficients vector} of the function $f$. Then $x f(x,y,z)$ is approximated by $\SHvec(x,y,z)^\top \: J_x^\top \: \fvec$. In other words, $J_x^\top \: \fvec$ is the coefficients vector for the expansion of the function $(x,y,z) \mapsto x \: f(x,y,z)$ in the spherical harmonics basis.

@@

Since the above holds for any $\Dlt$ that is a left inverse of $A_l$, we are free to choose the $\Dlt$ matrices in the following way. For $l \in \N$, we can set
\bseqnnumber{
	\Dlt = 
		\begin{pmatrix}
			& & & & & \vec{\eta}^\top_{0} \\
			0 & & & 0 & & & {1 \over \gamma_{l,-l,2}} & \\
			& \ddots & & & \ddots & & & \ddots \\
			& & 0 & & & 0 & & & {1 \over \gamma_{l,l,2}} \\
			& & & & & \vec{\eta}^\top_{1} 
		\end{pmatrix} \in \R^{(2n+3)\times3(2n+1)}, \label{eqn:Dltdef}
}
where $\vec{\eta}_{0}, \vec{\eta}_{1} \in \R^{3(2n+1)}$ are vectors with entries given by 
\bseqn{
	\big(\vec{\eta}_{0}\big)_j &= 
		\begin{cases}
			{1 \over \alpha_{l,-l,3}} & j = 1 \\
			{- \; \alpha_{l,-l,4} \over \alpha_{l,-l,3} \: \gamma_{l,1-l,2}} & j = 2(2n+1) + 2 \\
			0 & o/w
		\end{cases}, \\
	\big(\vec{\eta}_{1}\big)_j &= 
		\begin{cases}
			{1 \over \alpha_{l,l,4}} & j = 2l+1 \\
			{- \; \alpha_{l,l,3} \over \alpha_{l,l,4} \: \gamma_{l,l-1,2}} & j = 3(2n+1) - 1 \\
			0 & o/w
		\end{cases}.
}
For $l = 0$ we can simply set
\bseqnnumber{
	D^T_0 = 
		\begin{pmatrix}
			{\beta_{0,0,4} \over \alpha_{0,0,3} \beta_{0,0,4} - \alpha_{0,0,4} \beta_{0,0,3}} & {- \alpha_{0,0,4} \over \alpha_{0,0,3} \beta_{0,0,4} - \alpha_{0,0,4} \beta_{0,0,3}} & 0 \\
			0 & 0 & {1 \over \gamma_{0,0,2}} \\
			{\beta_{0,0,3} \over \alpha_{0,0,4} \beta_{0,0,3} - \alpha_{0,0,3} \beta_{0,0,4}} & {- \alpha_{0,0,3} \over \alpha_{0,0,4} \beta_{0,0,3} - \alpha_{0,0,3} \beta_{0,0,4}} & 0
		\end{pmatrix}. \label{eqn:Dzerotdef}
}
It will be convenient for us to give a formal name for these coefficient matrices above for a family of multidimensional orthogonal polynomials.
\begin{definition}\label{def:clenshawmats}
	The matrices $-\Dlt (B_l-G_l(x,y,z))$, $\Dlt C_l$ for $l \in \No$ defined via \bsrefeqns{eqn:clenshawmats1}{eqn:Dzerotdef} are called the recurrence coefficient matrices for a given family of multidimensional orthogonal polynomials.
\end{definition}
